Supplementary Materials for CBEA: Competitive Balances for Taxonomic Enrichment Analysis

### 2022-02-16 cbea_revised.tex
Updated funding

%\begin{figure}[!ht]
%    \centering
%    \includegraphics[width=\textwidth]{figures/sim_pred_rsq.png}
%    \caption{Predictive R-squared of a random forest model for a continuous outcome trained on CBEA,     %ssGSEA, GSVA generated scores as well as on standard CLR transformed data evaluated on simulated data %across sparsity levels, correlation, and signal-to-noise ratio. Panel \textbf{(A)} and \textbf{(B)} %represent results across different levels of model saturation (proportion of sets associated with the %outcome). CBEA approaches outperformed GSVA and ssGSEA but not standard CLR.}
%    \label{fig:sim_pred_rsq}
%\end{figure}

@@

\section*{Acknowledgments}
The authors thank Becky Lebeaux, Modupe Coker, Erika Dade, Jie Zhou, and Weston Viles for insightful comments and suggestions that greatly improved the paper. This work is supported by the National Institutes of Health (grants NCI R21CA253408, NIGMS P20GM130454, NCI P30CA023108, and NLM R01LM012723).

>>>>

@@

\section*{Acknowledgments}
The authors thank Becky Lebeaux, Modupe Coker, Erika Dade, Jie Zhou, and Weston Viles for insightful comments and suggestions that greatly improved the paper. Funding for HRF provided by National Institutes of Health grants R21CA253408, P20GM130454 and P30CA023108. Funding for AGH provided by National Institutes of Health grant R01LM012723. Funding for QPN provide by National Institutes of Health grants K01LM012426,
R21CA253408, P20GM130454, and R01LM012723. The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
